\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/mwong94}{\Large Maxwell Wong}} & Email : \href{mailto:mlwong2@uci.edu}{mlwong2@uci.edu}\\
  \href{https://github.com/mwong94}{https://github.com/mwong94} & Mobile : +1-858-431-9185 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UCI}{Irvine, CA}
      {Bachelor of Science in Data Science}{August 2015 -- Present}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {UCSD Keck Center for fMRI}{San Diego, CA}
      {Independent Research Intern}{January 2013 -- June 2014}
      \resumeItemListStart
        \resumeItem{Magnetic Resonance Fingerprinting}
          {MR Fingerprinting was a new MR image reconstruction method at the time.
          Independently validated the method, as well as explored its boundaries and properties.
          Presented my findings and an abstract at ISMRM 2015.}
        \resumeItem{Kernel based image reconstruction}
          {Implemented a kernel based MR image reconstruction algorithm using OpenCL for parallization.}
      \resumeItemListEnd
      \resumeSubheading
        {NIH/NIMH}{Bethesda, MD}
        {Summer Internship Program}{June 2017 -- September 2017}
        \resumeItemListStart
          \resumeItem{Semantic vector extraction}
            {Carried out research within a group to develop and optimize machine learning
            algorithms to extract semantic vector information from MR brain data.
            Participated in weekly lab meetings, and presented my findings at a NIH-wide
            poster day.}
        \resumeItemListEnd
        \resumeSubheading
          {Additive Manufacturing}{}
          {FDM/DLP 3D printing}{June 2016 -- Present}
          \resumeItemListStart
            \resumeItem{Industrial Additive Manufacturing}
              {Enrolled in an Additive Manufacturing course in the Engineering department.
              Worked with industrial 3D printing systems (Stratasys PolyJet/Fortus) as well
              as hobbyist style printers.}
            \resumeItem{Hobbyist Printing}
              {Built and maintain my own DIY FDM and DLP printers.}
          \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Reddit Front Page Predictor}
      {A two part project: (1) Reddit crawler to collect time series data into a
      PostgreSQL database on all posts in specified subreddits and (2) Machine Learning
      model to predict whether or not a post will eventually make it to the frontpage. \\
      {\sl https://github.com/mwong94/reddit}}
    \resumeSubItem{PDQ Android Game}
      {Developed a simple word game on Android built using Fragments, inspired by
      the card game PDQ. The game displays randomly generated problems, and provides
      solutions drawn from a SQLite database. \\
      {\sl https://github.com/mwong94/PDQFragment}}
  \resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item \textbf{Languages}{: Python, Java, C, C++, R, Bash, JSON, XML, Perl, YAML}
    \item \textbf{SQL}{: MySQL, PostgreSQL, SQLite}
    \item \textbf{Machine Learning}{: scikit-learn, Keras/TensorFlow, CNN, Autoencoders}
    \item{
      \textbf{Operating Systems Experience}{:  \resumeSubHeadingListStart
                                    \item{MacOS, Windows, UNIX (Linux and FreeBSD)}
                                    \item{Extensive experience with Debian, RedHat families
                                      (e.g. rebuilt lab's Ubuntu GPU compute server while at NIMH)}
                                    \item{Virtualization: QEMU, KVM, Xen, Proxmox, Docker}
                                    \item{Self hosted GitLab/OpenVPN/OpenSSH Docker server}
                                  \resumeSubHeadingListEnd}
    }
    \item \textbf{LaTeX}{: This resume is in LaTeX ({\sl https://github.com/mwong94/resume})}
    \item \textbf{Technologies}{: AWS, GCE, Beowulf clusters}
 \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
